---
title: "EAES 420 Midterm Starter"
author: "Nyla Williams"
date: "4/2/2024"
output: html_document
---

## Academic Honesty Statement

*I, \_\_\_\_\_\_\_\_\_\_\_\_\_, hereby state that I will not communicate with or gain information in any way from my classmates, or copy work from past assignments, during this exam, and that all work is my own.*

## Load packages

```{r load-packages, message = F}
library(tidyverse)
library(openintro)
```

## Exericses

### Exericse 1

[Enter code and/or narrative here.]
```{r}
glimpse(earthquakes)
```
 In this file, there are 123 Rows and 7 columns or variables. There are 5 numerical variables and 2 catergorical variables. 
 
### Exericse 2


```{r}
earthquake <- names(earthquakes)
```

Two stylistic choices for the names "earthquake : 
(1) Appropriate representation
(2) conciseness
### Exericse 3

```{r counting observations by region}
earthquakes %>% 
  count(region, sort = TRUE)
```
To Generate a similar output I could have used :

```{r}
earthquakes %>%
  group_by(region) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```

### Exericse 4

```{r}
highest_regions <- earthquakes %>%
  filter(region %in% c("Turkey", "Iran", "China", "Japan", "United States"))


ggplot(top_regions, aes(x = region)) +
  geom_bar() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


### Exericse 5

[Enter code and/or narrative here.]

### Exericse 6

[Enter code and/or narrative here.]

### Exericse 7

```{r visualize-earthquakes-deaths, eval = F}
earthquakes_subset %>% 
  ggplot(aes(x = month, y = deaths)) +
  geom_violin() +
  theme_classic()
```

[Enter code and/or narrative here.]

### Exericse 8

[Enter code and/or narrative here.]
